---
title: "02_UNCHAIN_dataanalysis"
author: "Linda Menk"
date: "20 1 2021"
output: 
  html_document:
    theme: flatly
    toc: true
    toc_float:
      collapsed: false
      smooth_scroll: false
      number_sections: true
---


```{r setup, include=FALSE, echo=FALSE, message=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
# Workflow  
## Open questions:  
- Lucias data = 1 km resolution. Land use data (Bodenbewertung, Grassland/Forest/Imperviousness change, Small Wooden Features has higher resolution (5m to 20m)). Shall we make really small Geons and focus on Lungau and Flachgau or should we aggregate the high resolution data to 1 km and use all of SBG? But then the high resolution data will be more or less useless. 
- Include Salzburg Stadt or not? (If not included Flachgau has a hole)

# Data acqusition  
## Sources
- RESPECT data  
- Copernicus Land Monitoring Service(mostly High-resolution datasets)

# Data exploration
## Quality check
This script encompasses the preprocessing steps necessary to use climate raster data for geonization in eCognition. It reads netCDF files, compares if the read files are of the same extent, crs, resolution, rotation and if they have the same number of columns and rows. It then standardizes the cell values to a mean of 0 and a sd of 1 to make values in different units (like # of heatdays and precipitation in mm) comparable. These values are then stretched to a 8-bit interval, in order to be fit for use in the remote sensing software "eCognition".It then writes the processed data to .tif files. Statistical info and visulaizations are plotted at the end of the script.

```{r libraries, echo=FALSE, message=FALSE, include=FALSE}
# Load libraries
library(terra)
library(ENMTools) # for correlation plot
library(raster)
library(knitr)
library(kableExtra)
library(corrplot)
library(ggplot2)
library(ggdist)
library(rasterVis)
library(plotly)
library(geodiv) #for kurtosis
library(dplyr)
library(magrittr)
```

```{r prepare agricultural mask}
crs_all<-"+proj=laea +lat_0=52 +lon_0=10 +x_0=4321000 +y_0=3210000 +ellps=GRS80 +units=m +no_defs"

Agri_mask <- vect("R:\\02_PROJECTS\\01_P_330001\\127_UNCHAIN\\03__Work\\WP4\\03_Casestudy\\02_Data\\Drought_data_Salzburg\\Bodenfunktionsbewertung_Shapefile\\Bodenfunktionsbewertung\\Bodenfunktionsbewertung.shp") %>% 
  project(crs_all)

Agri_mask$yes <- 20

Mask <- rast("R:\\02_PROJECTS\\01_P_330001\\127_UNCHAIN\\03__Work\\WP4\\03_Casestudy\\02_Data\\Mask_Salzburg_1km\\Mask_Salzburg_1km.tif") %>% 
  aggregate(fact = 10, fun = mean)

Agri_rast<-rasterize(Agri_mask, Mask, field ="yes", touches=TRUE)

plot(Agri_rast)

Agri_rast <- cover(Agri_rast, Mask)

Agri_rast[is.na(Agri_rast)] <- 255
Agri_rast[(Agri_rast == -1)] <- 255



# Visualization
Agri_rast_p <- raster(Agri_rast)
prim <- gplot(Agri_rast_p) + geom_tile(aes(fill=value), alpha=0.8) + coord_equal()+ scale_fill_gradient2(low = '#4cbb17', mid = '#f0e130', high ='#b7410e' , midpoint=128)+ggtitle("Agricultural area")
ggplotly(prim, tooltip= "value")

#--------------
# Export
export <- "R:\\02_PROJECTS\\01_P_330001\\127_UNCHAIN\\03__Work\\WP4\\03_Casestudy\\02_Data\\Mask_Salzburg_1km\\"
agri <- file.path(export,"Agri.tif")
terra::writeRaster(Agri_rast, agri, names = "Agri_mask", overwrite = TRUE)

```

```{r prepare final mask}

vul_path <- "R:\\02_PROJECTS\\01_P_330001\\127_UNCHAIN\\03__Work\\WP4\\03_Casestudy\\02_Data\\00_Final_data\\01_Vulnerability\\V\\"

vul_stack <- list.files(path = vul_path , pattern='.tif', all.files=TRUE, full.names = TRUE) %>% 
  rast()

#mask_0 <- rast("R:\\02_PROJECTS\\01_P_330001\\127_UNCHAIN\\03__Work\\WP4\\03_Casestudy\\02_Data\\Mask_Salzburg_1km\\Mask_SBG_only_1km.tif")
#agri_mask <- rast("R:\\02_PROJECTS\\01_P_330001\\127_UNCHAIN\\03__Work\\WP4\\03_Casestudy\\02_Data\\Mask_Salzburg_1km\\Agri.tif")


# We want mask to have the same projection and extent as vul_stack and forest_mask (they already match)
mask_1 <- project(Mask, vul_stack) %>% 
  crop(vul_stack)

# We remove everything from forest_mask which is not also in mask and then add 255 to NA area, so that the whole picture has either 255 or 0 as a value
# We mask everything from the forest_mask which is not contained in the mask (Germany and other areas outside of Salzburg). Outside Salzburg is NA, inside is 0 and forested areas are 255. We want also inside Salzburg to be NA. 
mask_2 <- terra::mask(Agri_rast, mask_1)

mask_2[mask_2==255] <- NA
```


# Vulnerability
```{r import Vulnerability data}

vul_path <- "R:\\02_PROJECTS\\01_P_330001\\127_UNCHAIN\\03__Work\\WP4\\03_Casestudy\\02_Data\\00_Final_data\\01_Vulnerability\\V\\"

vul_stack <- list.files(path = vul_path , pattern='.tif', all.files=TRUE, full.names = TRUE) %>% 
  rast()

vulnerability <- terra::mask(vul_stack, mask_2)
plot(vul_stack)
vulnerability[is.na(vulnerability)] <- 255

writeRaster(vulnerability,"R:\\02_PROJECTS\\01_P_330001\\127_UNCHAIN\\03__Work\\WP4\\03_Casestudy\\02_Data\\00_Final_data\\01_Vulnerability\\Stacks\\Vulnerability_stack.tif", overwrite = TRUE)
```
# 02_Exposure  
```{r import Exposure data}

exp_path <- "R:\\02_PROJECTS\\01_P_330001\\127_UNCHAIN\\03__Work\\WP4\\03_Casestudy\\02_Data\\00_Final_data\\02_Exposure\\"

exp_stack <- list.files(path = exp_path, pattern='.tif', all.files=TRUE, full.names = TRUE) %>% 
  rast()


exposure <- terra::mask(exp_stack, mask_2)
#plot(exposure)
exposure[is.na(exposure)] <- 255
plot(exposure)
writeRaster(exposure,"R:\\02_PROJECTS\\01_P_330001\\127_UNCHAIN\\03__Work\\WP4\\03_Casestudy\\02_Data\\00_Final_data\\02_Exposure\\Stacks\\Exposure_stack.tif", overwrite = TRUE)

```

# 03_Hazard: Variability
```{r import Hazard data}

haz_path <- "R:\\02_PROJECTS\\01_P_330001\\127_UNCHAIN\\03__Work\\WP4\\03_Casestudy\\02_Data\\00_Final_data\\03_Hazard\\"

haz_stack <- list.files(path = haz_path, pattern='.tif', all.files=TRUE, full.names = TRUE) %>% 
  rast() %>% 
  project(crs_all)
  
plot(haz_stack)
# 
# hazard <- terra::mask(haz_stack, mask_2)
# plot(hazard)
# hazard[is.na(hazard)] <- 255
# writeRaster(hazard,"R:\\02_PROJECTS\\01_P_330001\\127_UNCHAIN\\03__Work\\WP4\\03_Casestudy\\02_Data\\00_Final_data\\03_Hazard\\Stacks\\Hazard_stack.tif", overwrite = TRUE)
# 
haz_stack[haz_stack==255] <- NA
plot(haz_stack)
clip
writeRaster(haz_stack,"R:\\02_PROJECTS\\01_P_330001\\127_UNCHAIN\\03__Work\\WP4\\03_Casestudy\\02_Data\\00_Final_data\\03_Hazard\\Stacks\\Hazard_stack_for_pres.tif", overwrite = TRUE)
```

```{r hazard SPI}

spi_path <- "R:\\02_PROJECTS\\01_P_330001\\127_UNCHAIN\\03__Work\\WP4\\03_Casestudy\\02_Data\\01_ZAMG_SPARTACUS_Monthly\\Output\\Data\\SPI-6"

spi_stack <- list.files(path = spi_path, pattern='.tif', all.files=TRUE, full.names = TRUE) %>% 
  rast() %>% 
  project(mask_2)

spi_count <- subset(spi_stack, 1:6)
spi_delta <- subset(spi_stack, 7:10)


spi_count <- terra::mask(spi_count, mask_2)
spi_delta <- terra::mask(spi_delta, mask_2)
plot(spi_delta)
#spi[is.na(spi)] <- 255
writeRaster(spi_count,"R:\\02_PROJECTS\\01_P_330001\\127_UNCHAIN\\03__Work\\WP4\\03_Casestudy\\R_Scripts\\Risk_explorer_de\\data\\SPI_count_stack.tif", overwrite = TRUE)
writeRaster(spi_delta,"R:\\02_PROJECTS\\01_P_330001\\127_UNCHAIN\\03__Work\\WP4\\03_Casestudy\\R_Scripts\\Risk_explorer_de\\data\\SPI_delta_stack.tif", overwrite = TRUE)
```



```{r Missing values, echo=FALSE, message=FALSE, include=FALSE}
# Check for missing values

#shows NA values
NAvalue(data)

```

# Data exploration  
## Histograms, boxplots, descriptve statistics, correlation analysis, PCA    


 
```{r plotly, fig.width=10}
# Plot rasters interactive 

# Style the plot
austria<-gplot(vulnerability) + facet_wrap(~variable) +
  geom_tile(aes(fill=value)) + coord_equal()

#Plot the plot
ggplotly(austria)

```

```{r Descriptive statistics}
# Descriptive statistics 

apply(f, 1, cellStats)

f <-as(vul_stack,"Raster")

a<-cellStats(f, stat='mean', na.rm=TRUE)
b<-cellStats(f, stat='max', na.rm=TRUE)
c<-cellStats(f, stat='min', na.rm=TRUE)
d<-cellStats(f, stat='sd', na.rm=TRUE)
e<-cellStats(f, stat='skew', na.rm=TRUE)


g <- sku(f$V_Access,excess = TRUE)
h <- sku(f$V_SWF,excess = TRUE)
i <- sku(f$V_Organisms,excess = TRUE)
j <- sku(f$V_Fertile,excess = TRUE)
k <- sku(f$V_Wasserverh,excess = TRUE)
l <- sku(f$V_Gruenld,excess = TRUE)
m <- sku(f$V_Div_Plant,excess = TRUE)
n <- sku(f$V_Sealed,excess = TRUE)
o <- sku(f$V_Disadva,excess = TRUE)
p <- sku(f$V_Gastro,excess = TRUE)
q <- sku(f$V_Landschutz,excess = TRUE)
r <- sku(f$V_Naturschutz,excess = TRUE)
s <- sku(f$V_Wasser,excess = TRUE)

kurtosis <- c(g,h,i,j,k,l,m,n,o,p,q,r,s)
#define variable for naming of rows
vars <- names(subset)

#Assembling the single columns to one table
drought_indicators_statistics<-data.frame(
  "mean"=a,
  "max"=b,
  "min"=c,
  "std"=d,
  "skewness"=e,
  "kurtosis"=kurtosis
  )

#Visualizing the table
kable(drought_indicators_statistics, digits=2, col.names = c("mean","max","min","std","skewness","kurtosis")) %>% kable_styling(bootstrap_options = c("striped","bordered"), full_width = F) %>% 
  add_header_above(c("Layer Statistics" = 7))

```




```{r Histograms, message=FALSE, warning =FALSE, fig.height=12}
# Create histograms 
#Plot a histogram of original data

hist(subset, breaks = 25)#,zlim = c(0,50))

#Info histogram and bin settings
#https://www.earthdatascience.org/courses/earth-analytics/lidar-raster-data-r/plot-raster-histograms-r/

``` 


```{r Boxplot, echo=FALSE, message=FALSE, fig.width=10,fig.height=6}
# Create boxplot 

labels<-c("Population_density","Ecosystem_services","Land_use","Diversity_plants_agricult","Permanent_crops","Transport_infrastr")
par(mar=c(2,10,1,1))

#Boxplot original data all indicators
boxplot(subset,
main = "Boxplots RESPECT Drought data",
xlab = "Value Range",
#ylab = "Indicators",
col = "orange",
border = "brown",
horizontal = TRUE,
notch = FALSE,
varwidth = TRUE,
cex.axis=0.8,
las = 1
)

gplot(subset) + geom_tile(aes(fill = value)) + facet_wrap(~variable)+coord_equal()


```


```{r TIFF correlation matrix}

# Correlation Matrix Table ALL Data
data_rast <-  as(subset,"Raster")
#Calculating correlation matrix from all rasters
correlation<-raster.cor.matrix(data_rast, method = "spearman")
raster.cor.plot(data_rast)$cor.mds.plot
raster.cor.plot(data_rast)$cor.heatmap


#Visualizing the table
kable(correlation,digits=2) %>% kable_styling(bootstrap_options = c("striped","bordered"), full_width = T)

corrplot(as.matrix(correlation), method = "square", type = "lower", sig.level = 0.05,  tl.cex = 0.7, tl.col = "black", tl.srt = 45, number.cex = 0.7, addCoef.col = TRUE, addCoefasPercent = TRUE, order = "FPC")


#Step 1: converts the R table into a dataframe
export_tab<-as.data.frame.matrix(correlation)
#Step 2: Exports the DataFrame to CSV
#write.csv(export_tab, "C:\\Users\\b1012771\\Desktop\\hotspotdata_20201013_correlation.csv",row.names = TRUE)

X<-wagesmicrodata[,3:12]
library(GGally)
ggpairs(subset)

```



